The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-23 paper/sections/methods.tex
blah

 \begin{equation}
    \defX\left(\refX\right) = \sum_{\prt_i\in\Prts} \bld_i\Pmatxi\Pi_i\vc{q}_i, 
 \end{equation} where $w_i$ $\Pmatx_i$, $\Pi_i$ and $\vc{q}_i$ are the blending weights, polynomial basis, projection operator and control points for the $i^{th}$
 part respectively.

@@

\subsection{Meshless Blending Weight Computation}
\label{sec:weights}

\subsection{Choosing Deformation Centers}
\label{sec:origins}

%%%% OLD STUFF BELOW HERE  %%%%%
\subsection{Blending Weights}
\dave{Desireable Properties}
\dave{Construction via post normalization}
\dave{only need blending weights at quadrature points and surface samples so given sparse set of quadrature points compute blending weights using raycasting}
\dave{things to explain (1) raycasting works for overlapping geometric, seperated geometry (2) weights glue objects together}
\dave{maybe but weight figure here so reviewers immediately know that it looks pretty good}
All that remains for the deformation map is to compute blending weights. Our choice of the weighting function is guided by the simple idea that that for a given material point its weight should be highest to whichever surfaces it is closest. This idea lends itself to a simple distance-based weighting method. The first step in this process is to compute \textit{distance weights}. For a given point $\mathbf{X}$ and a set of $n$ we wish to compute a set of distance weights to each surface $\mathbf{\theta}(\mathbf{X}) = \left(\theta_1, \dots, \theta_i, \dots, \theta_n \right)$.

@@

\subsection{Multiple Part Projection}
\dave{explain why you need to share constant terms (fit polynomial around a point in space), explain clustering and how to pick, forward reference to quadrature point}
\subsection{Quadrature Points}
\dave{quadrature via raycasting}
The last step before we may discuss the dynamic simulation is to describe our strategy for generating material points $\mathbf{X}$ in the undeformed model. Our volume integration strategy is based on \cite{KHOSRAVIFARD201030} which we briefly describe in the following section

>>>>

 \begin{equation}
    \defX\left(\refX\right) = \sum_{\prt_i\in\Prts} \bld_i\Pmatxi\Pi_i\vc{q}_i, 
    \label{eq:kinematics}
 \end{equation} where $w_i$ $\Pmatx_i$, $\Pi_i$ and $\vc{q}_i$ are the blending weights, polynomial basis, projection operator and control points for the $i^{th}$
 part respectively.

@@

\subsection{Choosing Deformation Centers}
\label{sec:origins}
\dave{Ty: try to follow this formula when writing 
(1) what is the purpose of this part of the method ?
(2) what are the criteria for success
(3) what is our assumed input 
(4) what is the desired output
(5) what's the algorith,
(6) add proofs/diagrams/figures that show we satisfy (2). }

\subsection{Meshless Blending Weight Computation}
\label{sec:weights}
\dave{Desireable Properties}
\dave{Construction via post normalization}
\dave{only need blending weights at quadrature points and surface samples so given sparse set of quadrature points compute blending weights using raycasting}
\dave{things to explain (1) raycasting works for overlapping geometric, seperated geometry (2) weights glue objects together}
\dave{maybe but weight figure here so reviewers immediately know that it looks pretty good}
\dave{need to mention Monte Carlo Geometry processing but can't use it because our parts can overlap and that's a tricky boundary condition}

All that remains for the deformation map is to compute blending weights. Our choice of the weighting function is guided by the simple idea that that for a given material point its weight should be highest to whichever surfaces it is closest. This idea lends itself to a simple distance-based weighting method. The first step in this process is to compute \textit{distance weights}. For a given point $\mathbf{X}$ and a set of $n$ we wish to compute a set of distance weights to each surface $\mathbf{\theta}(\mathbf{X}) = \left(\theta_1, \dots, \theta_i, \dots, \theta_n \right)$.

@@

\subsection{Quadrature Points}
\dave{quadrature via raycasting}
The last step before we may discuss the dynamic simulation is to describe our strategy for generating material points $\mathbf{X}$ in the undeformed model. Our volume integration strategy is based on \cite{KHOSRAVIFARD201030} which we briefly describe in the following section
